Spatiotemporal transmission risk

### 2023-03-09 analysis/spatiotemporal-transmission-risk.Rmd
Update preprocessing, descriptive plots, and utils

```{r}
library(tidyverse)
library(reshape2)
library(LaplacesDemon)
library(rriskDistributions)
library(tidybayes)
library(lubridate)
library(sf)
library(raster)
library(terra)
library(ggridges)
library(ggplot2)

source("../utils/distr.r")
source("../utils/trans_risk.r")
source("../utils/spatial.r")
source("../utils/plotting.R")
```

@@

@@

* Ko et al. (2004): exponential decrease on an airplane, but they are more strongly ventilated
* Abkarian et al. (2020) deduce that, for the respiratory jet generated by typical speaking, the concentration of pathogen is diminished to approximately 3% of its initial value at a distance of 2 m.
* SSPH report: distance depends on size of aerosols and initial speed, which depends on the activity. For speaking, it will be around 1-2m, for coughing or sneezing it can be up to 7-8m
* Wang et al. (2021) and other studies: viral concentration is highest closest to the source

@@

```{r}
rMuIc <- function(n) {
  rgamma(n, shape = 10, scale = .2)
}

hist(rMuIc(1e3))

dIc <- function(distance, mu) { 
  1 - pexp(distance, 1 / mu)
}

expand.grid(distance = seq(0, 10, .1), rate = rMuIc(1e3)) %>%
  mutate(dens_inf = dIc(distance, rate)) %>%
  ggplot(aes(x = distance, y = dens_inf)) +
  stat_lineribbon() +
  scale_fill_brewer() +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) 
```

@@

* Catanzaro (1982): 249 quanta/h 
* Nardell (1991): 12.7 quanta/h
* Riley (1962): 1.25 quanta/h but patients already started on chemotheraphy and also few highly infectious patients
* Escombe (2008): 8.2 quanta/h but wide range, including an extreme outlier of 226 quanta/h
* Andrews (2014): 0.44 to 5.69 quanta/h

--> The distribution should roughly reflect the following quantiles
* <1: 10%
* <5: 50%
* <10: 75%
* <50: 95%
* <100: 99%

```{r}
q_a <- c(1, 5, 10, 50, 100, 200)
p_a <- c(.1, .5, .75, .95, .99, 1)
q_range <- seq(0, 200, .1)
p_q_range <- ptrunc(q_range, spec = "st", a = 0, b = 300, mu = 4, sigma = 4, nu = 1)
p_a_selected <- ptrunc(q_a, spec = "st", a = 0, b = 300, mu = 4, sigma = 4, nu = 1)
lnorm_par <- inv_lnorm_moments(5, 10)
p_q_range_lnorm <- plnorm(q_range, meanlog = lnorm_par$meanlog, sdlog = lnorm_par$sdlog)

ggplot(mapping = aes(x = q_range)) +
  geom_line(mapping = aes(y = p_q_range), color = "black") +
  geom_line(mapping = aes(y = p_q_range_lnorm), color = "red") +
  geom_point(mapping = aes(x = q_a, y = p_a_selected), color = "black") +
  geom_point(mapping = aes(x = q_a, y = p_a), color = "blue") +
  scale_x_log10(breaks = q_a) +
  scale_y_continuous(breaks = p_a)

rq <- function(n) {
  rtrunc(n, spec = "st", a = 0, b = 300, mu = 4, sigma = 4, nu = 1)
}

dq <- function(x) {
  dtrunc(x, spec = "st", a = 0, b = 300, mu = 4, sigma = 4, nu = 1)
}

rq_distr <- data.frame(quanta = seq(0, 100, .1)) %>% mutate(prob = dq(quanta))

ggplot(rq_distr, aes(x = quanta, y = prob)) +
  geom_line()
```

### Average volume of exhaled gas

* Richardson et al. (2014): 0.1 - 1.17 l/s per person based on Feher (2017)

```{r}
rV <- function(n) {
  runif(n, 0.1, 0.17)
}
```

### Loss rate due to inactivation

@@

### Loss rate due to deposition onto surfaces

@@

### CO2 levels in outdoor air

* https://gml.noaa.gov/dv/data/index.php?site=CPT&parameter_name=Carbon%2BDioxide,%20accessed%2012%20November%202019

```{r}
co2_outdoor <- 412.5
```

### CO2 levels in exhaled air

* Rudnick and Milton (2003): 40,000

```{r}
co2_exhaled <- 40000
```

### CO2 generation rate

* Persily et al.: see Table 5, around 0.003 to 0.005

```{r}
rG <- function(n) {
  runif(n, 0.0041, 0.0055)
}
```

* Masked TB patients: TB suspects
* Unmasked TB patients: Poisson(mu = TB suspects)

```{r}
rTBunmasked <- function(n, lambda) {
  rpois(n, lambda)
}
```

```{r}
# clinical data
clinXov <- readRDS("../data-clean/Masi/merged-clinical-xovis.rds")

yesTB <- clinXov %>%
  filter(tb_suspect=="yes") %>%
  group_by(patient_id) %>%
  slice(1) %>%
  ungroup()

nTBmasked <- nrow(yesTB)

noTB <- clinXov %>%
  dplyr::filter(ifelse(is.na(tb_suspect), T, ifelse(tb_suspect=="no", T, F))) %>%
  group_by(person_id) %>%
  slice(1) %>%
  ungroup()

# Time period (for the first day)
time_period <- seq(min(as.POSIXct(format(clinXov$time, "%Y-%m-%d %H:%M"))), 
                   max(as.POSIXct(format(clinXov$time, "%Y-%m-%d %H:%M"))), 
                   by = "min")
```

### Co2

```{r}
# co2
co2 <- readRDS("../data-clean/Masi/environmental-data/co2-levels.rds") %>%
  filter(date == "2021-10-25") 
#' assume waiting area has mean co2 of waiting room and registration
#' passage has co2 of watiing room only
#' tb room has co2 of tb room only
co2 <- co2 %>%
  filter(location %in% c("waiting room", "registration")) %>%
  group_by(date_time) %>%
  summarize(co2 = mean(co2)) %>%
  ungroup() %>%
  mutate(location = "waiting room") %>%
  rbind(co2 %>%
          filter(location == "waiting room") %>%
          mutate(location = "passage") %>%
          dplyr::select(date_time, location, co2)) %>%
  rbind(co2 %>%
          filter(location == "TB room") %>%
          mutate(location = "tb room") %>%
          dplyr::select(date_time, location, co2)) 
ggplot(co2, aes(x = date_time, y = co2, color = location)) + geom_line()
```

### Room

```{r}
# choose cell size such that the squared cell has 1m3 volume
cellVolume <- 1
cellSize <- sqrt(cellVolume * 1e9 / 3e3)

# waiting room
sh_wr <- vect("../data-raw/Masi/building/waiting_room.shp")
sf_wr <- st_as_sf(sh_wr)
wrRoomSP <- shapeToSpatial(sh_wr, cellSize)
wrVol <- compute_volume(wrRoomSP)
wrCellCoords <- create_coord_df(wrRoomSP)
wrRoomXY <- as.matrix(dplyr::select(wrCellCoords, x, y))

# tb room
sh_tb <- vect("../data-raw/Masi/building/tb_room.shp")
sf_tb <- st_as_sf(sh_tb)
tbRoomSP <- shapeToSpatial(sh_tb, cellSize)
tbVol <- compute_volume(tbRoomSP)
tbCellCoords <- create_coord_df(tbRoomSP)
tbRoomXY <- as.matrix(dplyr::select(tbCellCoords, x, y))

# passage
sh_pa <- vect("../data-raw/Masi/building/passage.shp")
sf_pa <- st_as_sf(sh_pa)
paRoomSP <- shapeToSpatial(sh_pa, cellSize)
paVol <- compute_volume(paRoomSP)
paCellCoords <- create_coord_df(paRoomSP)
paRoomXY <- as.matrix(dplyr::select(paCellCoords, x, y))

# combine
clinicCellCoords <- rbind(
  mutate(wrCellCoords, location = "waiting room"),
  mutate(tbCellCoords, location = "tb room"),
  mutate(paCellCoords, location = "passage")
) %>% mutate(id = 1:nrow(.))
clinicCellCoordsXY <- cbind(clinicCellCoords$x, clinicCellCoords$y)
```

```{r}
# number of people in space
nDF <- tibble()
for (tp in time_period) {
  n_tp <- clinXov %>%
    filter(between(time, tp, tp + seconds(59))) %>%
    mutate(location = mapply(function(x,y) clinicCellCoords$location[find_raster(x,y,clinicCellCoordsXY)], x, y)) %>%
    group_by(person_id, location) %>%
    slice(1) %>%
    ungroup() %>%
    group_by(location) %>%
    summarize(n = n()) %>%
    ungroup() 
  for (loc in unique(clinicCellCoords$location)) {
    if (!(loc %in% n_tp$location)) {
      n_tp <- rbind(n_tp, data.frame(location = loc, n = 0))
    } 
  }
  nDF <- rbind(nDF, n_tp %>% mutate(time = tp))
}
nDF <- nDF %>% 
  mutate(time = as.POSIXct(time, origin = as.Date("1970-01-01")))
nDF$n[nDF$location=="waiting room"] <- nDF$n[nDF$location=="waiting room"] + nDF$n[nDF$location=="passage"]
nDF$n[nDF$location=="passage"] <- nDF$n[nDF$location=="waiting room"] + nDF$n[nDF$location=="passage"]
ggplot(nDF, aes(x = time, y = n, color = location)) + geom_line()
```

### Movement

```{r}
patMov <- clinXov %>%
  mutate(id = map2_int(x, y, find_raster, cellCoordsXY = clinicCellCoordsXY))
```

>>>>

```{r}
library(tidyverse)
library(reshape2)
library(rriskDistributions)
library(tidybayes)
library(lubridate)
library(sf)
library(raster)
library(terra)
library(ggridges)
library(grid)
library(ggplot2)
library(ggrepel)

source("../utils/distr.r")
source("../utils/trans_risk.r")
source("../utils/spatial.r")
source("../utils/plotting.R")

# plot with and height of input and data graphs
aw <- 12
ah <- 8
```

```{r}
clinical_dta <- readRDS("../data-clean/Masi/clinical-data/clinical-data.rds")
share_tb <- clinical_dta %>%
  group_by(date, patient_id) %>%
  summarize(tb = any(tb_suspect == "yes")) %>%
  ungroup() %>%
  group_by(date) %>%
  summarize(n = n(),
            n_tb = sum(tb)) %>%
  arrange(date) %>%
  mutate(prop_tb = n_tb / n * 100,
         date = format(date, format = "%b %d"),
         date = factor(date, levels = unique(date))) %>%
  ungroup() 
share_tb_pl <- share_tb %>%
  ggplot(aes(x = date, y = n_tb)) +
  geom_bar(stat = "identity", fill = "grey", color = "black", width = .5) +
  annotate("text", x = "Nov 09", y = mean(share_tb$n_tb), label = paste0("Mean = ",round(mean(share_tb$n_tb), 1)), color = "darkred", size = 8 / cm(1), vjust = -1) +
  geom_hline(aes(yintercept = mean(share_tb$n_tb)), color = "darkred") +
  scale_y_continuous(expand = expansion(mult = c(0,0.05))) +
  scale_x_discrete(breaks = c("Oct 11", "Oct 18", "Oct 25", "Nov 02", "Nov 09", "Nov 16")) +
  labs(y = "No. of TB patients") +
  theme_bw2() +
  theme(axis.title.x = element_blank(),
        plot.margin = margin(5.5, 10, 5.5, 5.5))
save_plot(share_tb_pl, pdf_file = "../results/data/share-tb-patients.pdf", w = aw, h = ah)
```

### CO2

```{r}
co2_pl <- readRDS("../data-clean/Masi/environmental-data/co2-temp-humid.rds") %>%
  filter(location %in% c("waiting room", "tb room")) %>%
  mutate(location = factor(ifelse(location == "tb room", "TB room", "Waiting room"), levels = c("Waiting room", "TB room")),
         time = as.POSIXct(time, format = "%H:%M", tz = "CET")) %>%
  ggplot(aes(x = time, y = co2, color = location, fill = location)) +
  stat_lineribbon(alpha = .25, size = .5) +
  scale_x_datetime(expand = c(0,0), date_breaks = "2 hours", date_labels = "%H:%M") +
  scale_y_continuous(expand = c(0,0), breaks = scales::breaks_width(width = 100)) +
  scale_fill_brewer(palette = "Accent") +
  scale_color_brewer(palette = "Accent") +
  labs(y = expression("CO"[2]*" (ppm)"), fill = "Quantile", color = "Quantile") +
  theme_bw2() +
  theme(legend.position = c(.8,.95), legend.direction = "horizontal", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        plot.margin = margin(5.5, 10, 5.5, 5.5), axis.title.x = element_blank(), legend.title = element_blank()) 
save_plot(co2_pl, pdf_file = "../results/data/co2-levels.pdf", w = aw, h = ah)
```

### Building

```{r}
# background image
clinic_img <- png::readPNG("../data-raw/Masi/building/clinic_clipped.png")
```

<!-- ```{r} -->
<!-- # choose cell size such that the squared cell has 1m3 volume -->
<!-- cellVolume <- 1 -->
<!-- cellSize <- sqrt(cellVolume * 1e9 / 3e3)  -->

<!-- # waiting room -->
<!-- sh_wr <- vect("../data-raw/Masi/building/waiting_room.shp") -->
<!-- sf_wr <- st_as_sf(sh_wr) -->
<!-- wrRoomSP <- shapeToSpatial(sh_wr, cellSize) -->
<!-- wrVol <- compute_volume(wrRoomSP) -->
<!-- wrCellCoords <- create_coord_df(wrRoomSP) -->
<!-- wrRoomXY <- as.matrix(dplyr::select(wrCellCoords, x, y)) -->

<!-- # tb room -->
<!-- sh_tb <- vect("../data-raw/Masi/building/tb_room.shp") -->
<!-- sf_tb <- st_as_sf(sh_tb) -->
<!-- tbRoomSP <- shapeToSpatial(sh_tb, cellSize) -->
<!-- tbVol <- compute_volume(tbRoomSP) -->
<!-- tbCellCoords <- create_coord_df(tbRoomSP) -->
<!-- tbRoomXY <- as.matrix(dplyr::select(tbCellCoords, x, y)) -->

<!-- # passage -->
<!-- sh_pa <- vect("../data-raw/Masi/building/passage.shp") -->
<!-- sf_pa <- st_as_sf(sh_pa) -->
<!-- paRoomSP <- shapeToSpatial(sh_pa, cellSize) -->
<!-- paVol <- compute_volume(paRoomSP) -->
<!-- paCellCoords <- create_coord_df(paRoomSP) -->
<!-- paRoomXY <- as.matrix(dplyr::select(paCellCoords, x, y)) -->

<!-- # combine -->
<!-- clinicCellCoords <- rbind( -->
<!--   mutate(wrCellCoords, location = "waiting room"), -->
<!--   mutate(tbCellCoords, location = "tb room"), -->
<!--   mutate(paCellCoords, location = "passage") -->
<!-- ) %>% mutate(id = 1:nrow(.)) -->
<!-- clinicCellCoordsXY <- cbind(clinicCellCoords$x, clinicCellCoords$y) -->
<!-- ``` -->

```{r}
files <- list.files("../data-clean/Masi/patient-tracking-data/", full.names = T)
no_people <- do.call(rbind, lapply(files, function(x) readRDS(paste0(x, "/patient-id-data.rds")))) %>%
  mutate(date = format(time, format = "%Y-%m-%d"),
         time = as.POSIXct(time, format = "%H:%M", tz = "CET"),
         daytime = ifelse(time <= "2021-10-25 12:00:00", "Morning", "Afternoon"),
         daytime = factor(daytime, levels = c("Morning", "Afternoon")))

# over time
no_people_time_pl <- no_people %>%
  group_by(date, time) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  ggplot(aes(x = time, y = n)) +
  geom_line() +
  #stat_lineribbon(alpha = .25, size = .5) +
  scale_x_datetime(expand = c(0,0), date_breaks = "2 hours", date_labels = "%H:%M") +
  scale_y_continuous(expand = c(0,0), limits = c(0, NA), breaks = scales::breaks_width(5)) +
  scale_fill_brewer(palette = "OrRd") +
  labs(y = "No. of clinical attendees") +
  theme_bw2() +
  theme(axis.title.x = element_blank())
  #labs(y = "No. of clinical attendees", fill = "Quantile", color = "Quantile") +
  # theme(legend.position = c(.8,.9), legend.direction = "horizontal", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
  #       plot.margin = margin(5.5, 10, 5.5, 5.5)) +
  # guides(fill = guide_legend(title.position = "top"))
save_plot(no_people_time_pl, pdf_file = "../results/data/no-people-over-time.pdf", w = aw, h = ah)

# Spatial
no_people_spatial_pl <- no_people %>%
  dplyr::select(x, y) %>%
  adespatial::rotation(angle = -8*pi/180) %>%
  as.data.frame() %>%
  set_names(c("x", "y")) %>%
  mutate(x = -x) %>%
  ggplot(aes(x = x, y = y)) +
  geom_bin2d(binwidth = 100) +
  ggpubr::background_image(clinic_img) +
  annotate("text", x = -13200, y = -5300, label = "Entrance", size = 8 / cm(1), fontface = 2, hjust=0,vjust=0) +
  annotate("text", x = -13400, y = -2300, label = "Waiting room", size = 8 / cm(1), fontface = 2, hjust=0,vjust=0) +
  annotate("text", x = -5000, y = -4100, label = "Registration", size = 8 / cm(1), fontface = 2, angle = 90, hjust=0,vjust=0) +
  annotate("text", x = 2600, y = -2700, label = "TB room", size = 8 / cm(1), fontface = 2) +
  scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")[c(1,3,5,7,9)], breaks = c(1,5,10,50,100), limits = c(0,100)) +
  scale_y_continuous(expand = expansion(mult = c(0,.18))) +
  scale_x_continuous(expand = expansion(mult = c(0,0.025))) +
  labs(fill = "Density") +
  theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),
        legend.position = c(0.825,0.075), legend.direction = "horizontal", legend.title = element_blank(), #legend.title = element_text(vjust = .75),
        panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 3, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
save_plot(no_people_spatial_pl, pdf_file = "../results/data/no-people-spatial.pdf", w = aw, h = ah)
```

<!-- ```{r} -->
<!-- # number of people in space -->
<!-- nDF <- tibble() -->
<!-- for (tp in time_period) { -->
<!--   n_tp <- clinXov %>% -->
<!--     filter(between(time, tp, tp + seconds(59))) %>% -->
<!--     mutate(location = mapply(function(x,y) clinicCellCoords$location[find_raster(x,y,clinicCellCoordsXY)], x, y)) %>% -->
<!--     group_by(person_id, location) %>% -->
<!--     slice(1) %>% -->
<!--     ungroup() %>% -->
<!--     group_by(location) %>% -->
<!--     summarize(n = n()) %>% -->
<!--     ungroup()  -->
<!--   for (loc in unique(clinicCellCoords$location)) { -->
<!--     if (!(loc %in% n_tp$location)) { -->
<!--       n_tp <- rbind(n_tp, data.frame(location = loc, n = 0)) -->
<!--     }  -->
<!--   } -->
<!--   nDF <- rbind(nDF, n_tp %>% mutate(time = tp)) -->
<!-- } -->
<!-- nDF <- nDF %>%  -->
<!--   mutate(time = as.POSIXct(time, origin = as.Date("1970-01-01"))) -->
<!-- nDF$n[nDF$location=="waiting room"] <- nDF$n[nDF$location=="waiting room"] + nDF$n[nDF$location=="passage"] -->
<!-- nDF$n[nDF$location=="passage"] <- nDF$n[nDF$location=="waiting room"] + nDF$n[nDF$location=="passage"] -->
<!-- ggplot(nDF, aes(x = time, y = n, color = location)) + geom_line() -->
<!-- ``` -->

<!-- ### Movement -->

<!-- ```{r} -->
<!-- patMov <- clinXov %>% -->
<!--   mutate(id = map2_int(x, y, find_raster, cellCoordsXY = clinicCellCoordsXY)) -->
<!-- ``` -->

@@

```{r}
n_samples <- 1000
set.seed(12345)
```

@@

* Wang (2021): 
  * Travel distance of particles depends on particle size, activity, and environmental factors
  * Smaller aerosols can travel further, stay in the air for a longer time, and typically contain higher viral load
  * The concentration of exhaled aerosols is highest close to the source and decreases with distance
  * Short-range aerosol transmission difficult to prevent with ventilation
* Chen (2020): Short-range aerosols dominate over most distance up to 2m, droplets only play a role at very close distance <0.5
* Ko (2004): exponential decrease of potential infections on an airplance (high ventilation) with distance to infector

@@

```{r}
relQC_pl <- expand.grid(distance = seq(0, 10, .1), 
                           mu = rMuIc(n_samples)) %>%
  mutate(relQC = dIc(distance, mu) * 100) %>%
  ggplot(aes(x = distance, y = relQC)) +
  stat_lineribbon(alpha = .5, size = .5) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_brewer(palette = "OrRd") +
  labs(x = "Distance (m)", y = "Relative quanta concentration (%)", fill = "Quantile") +
  theme_bw2() +
  theme(legend.position = c(.8,.9), legend.direction = "horizontal", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        plot.margin = margin(5.5, 10, 5.5, 5.5)) +
  guides(fill = guide_legend(title.position = "top"))
save_plot(relQC_pl, pdf_file = "../results/inputs/spatial-relative-quanta-concentration.pdf", w = aw, h = ah)
```

@@

* Riley (1962): 130 patients, q: 1.25
* Escombe (2008): 117 patients, q: 8.2; but high values above 100 are possible
* Nardell (1991) : 1 patients, q: 12.5
* Andrews (2014) : 571 patients, q: 0.89

--> Take the mean and standard deviation of these values and use a student-t distribution with small degrees of freedom to consider outliers

```{r}
q <- c(1.25, 8.2, 12.5, 0.89)
n_q <- c(130, 117, 1, 571)
mean_q <- sum(n_q * q) / sum(n_q)
sd_q <- sqrt( sum( (n_q / sum(n_q) * (q - mean_q) ^ 2 ) ) )

qLiterature <- data.frame(q = q, 
                          y = .01, 
                          lab = c("Riley", "Escombe", "Nardell", "Andrews"))

q_pl <- data.frame(q = seq(0, 40, .1)) %>%
  mutate(density = dq(q)) %>%
  ggplot(aes(x = q, y = density)) +
  geom_line() +
  geom_vline(mapping = aes(xintercept = 2), linetype = "dashed", color = "darkred") +
  annotate("text", x = 3, y = 0.175, hjust = 0, label = "Mean = 2.0", size = 8 / cm(1), color = "darkred") +
  geom_point(data = qLiterature, mapping = aes(x = q, y = y, color = lab, shape = lab)) +
  geom_text_repel(data = qLiterature, mapping = aes(x = q, y = y, color = lab, label = lab), size = 8 / cm(1)) +
  annotate("text", x = 30, y = 0.175, label = expression("q ~ Student-t("*mu*"=2.0,"*sigma*"=2.5"*","*nu*"=1)"), size = 8 / cm(1)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 40)) +
  scale_y_continuous(expand = expansion(mult = c(0,0.05))) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  labs(x = "Quanta emission (log q/h)", y = "Density") +
  theme_bw2() +
  theme(plot.margin = margin(5.5, 10, 5.5, 5.5), legend.position = "none")
save_plot(q_pl, pdf_file = "../results/inputs/quanta-emission.pdf", w = aw, h = ah)
```

* Berhanu (2023): 
  * study group: clinic attendees living with HIV, contact with TB patients in past year, or had TB in the past 2 years
  * finding: 55% of  with a sputum result positive for M. tuberculosis did not have a positive TB symptom screen
* Hamada (2018): The WHO 4-question symptom screen (cough, fever, weight loss, and night sweats) misses up to half the TB cases among people living with human immunodeficiency virus (HIV) on antiretroviral therapy (ART)
--> Unmasked TB patients: Poisson(mu = No. of TB suspects)

```{r}
unmaskedTB <- data.frame(n_tb = share_tb$n_tb) %>%
  mutate(unmasked_tb = lapply(n_tb, function(x) rTBunmasked(n = n_samples, lambda = x))) %>%
  unnest(unmasked_tb) %>%
  group_by(unmasked_tb) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(prop_unmasked_tb = n / sum(n)) 
mean_unmaskedTB <- sum(unmaskedTB$unmasked_tb * unmaskedTB$prop_unmasked_tb)
unmaskedTB_pl <- unmaskedTB %>%
  ggplot(aes(y = prop_unmasked_tb, x = unmasked_tb)) +
  geom_bar(stat="identity", fill = "grey", color = "black") +
  geom_vline(mapping = aes(xintercept = mean_unmaskedTB), linetype = "dashed", color = "darkred") +
  annotate("text", y = 0.25, x = mean_unmaskedTB, hjust = -.2, label = paste0("Mean = ", round(mean_unmaskedTB, 1)), size = 8 / cm(1), color = "darkred") +
  scale_y_continuous(expand = expansion(mult = c(0,0.05))) +
  scale_x_continuous(expand = c(0,0)) +
  labs(x = "No. of unmasked TB patients", y = "Probability (%)") +
  theme_bw2()
save_plot(unmaskedTB_pl, pdf_file = "../results/inputs/unmasked-tb-patients.pdf", w = aw, h = ah)
```

### Ventilation

Average volume of exhaled gas:
* Richardson et al. (2014): 0.1 - 0.17 l/s per person based on Feher (2017)
--> Use Uniform(0.1, 0.17)

CO2 levels in outdoor air:
* https://gml.noaa.gov/dv/data/index.php?site=CPT&parameter_name=Carbon%2BDioxide,%20accessed%2012%20November%202019
--> Set to 4125.5

CO2 levels in exhaled air:
* Rudnick and Milton (2003): 40,000
--> Set to 40,000

CO2 generation rate
* Persily et al.: see Table 5, around 0.003 to 0.005
--> Use Uniform(0.003, 0.005)

### Inactivation

@@

### Deposition onto surfaces

@@
